Quality assurance of digital twins: An experience report in the automotive industry

### 2023-07-04 manuscripts/paper-1/Without_Names.tex
Consistent

    \subsection{Digital twin quality}
    To analyze the state of the digital twin quality, a literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations. Therefore, various tools, such as Scopus and Google Scholar were 
    used to perform an extensive literature analysis on digital twin publications. However, due to the vast amount of available literature, the scope of the research was narrowed down, resulting in the identification of 
    150 dissertations linked to digital twin quality, verification and validation. After a thorough review of these, only 17 were considered relevant for this paper, and as a result following findings were revealed.

@@

    As a result, a total of twenty-one quality issues were identified, listed, and finally mapped to the digital twin quality attributes (Table~\ref{tab:Table1}) (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).

>>>>

    \subsection{Digital Twin Quality}
    To analyze the state of the digital twin quality, a literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations. Therefore, various tools, such as Scopus and Google Scholar were 
    used to perform an extensive literature analysis on digital twin publications. However, due to the vast amount of available literature, the scope of the research was narrowed down, resulting in the identification of 
    150 dissertations linked to digital twin quality, verification and validation. After a thorough review of these, only 17 were considered relevant for this paper, and as a result following findings were revealed.

@@

    As a result, a total of twenty-one quality related issues were identified, listed, and finally mapped to the digital twin quality attributes (Table~\ref{tab:Table1}) (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
